\begin{abstract}
We put forth a \emph{keyless wallet}, a cryptocurrency wallet
where money can be spent using a password alone, and no private
keys are required.
It requires a smart contract blockchain.
We propose two schemes. In the first, the user sets a short wallet password
and can spend their money at a prespecified maturity date using the
password alone. Using this as a stepping stone, we propose
a second scheme, in which the user uses an OTP authenticator seed to
generate a long series of time-based OTP passwords for the foreseeable
future.  These are encrypted and organized in a Merkle tree whose root is stored in a
smart contract.
The user can spend funds at any time by simply visually providing
the current OTP password from an air gapped device.
These OTPs can be relatively short:
Just $6$ alphanumeric characters suffice.
Our OTP scheme can work in proof-of-stake as well as
static and variable difficulty proof-of-work blockchains.
The low-entropy passwords and OTPs in our scheme are protected
from brute force attacks by requiring that an adversary accompany
any attempt by a transaction on the chain. This quickly
incurs enormous economic costs for the adversary. Thus, we develop the first decentralized
\emph{rate limiting} scheme.
We use
\emph{Witness Encryption} (WE) to construct a timelock encryption scheme
in which passwords are encrypted from past into future blocks
by leveraging the \textsc{NP}-language having
proof-of-work or proof-of-stake performed as the witness. Witness Encryption is
a currently impractical cryptographic primitive,
but our scheme may become practical
as these primitives are further developed.
\end{abstract}
